Report

### 2021-05-28 Rmd/report.Rmd
Try to fix (finally)

#### Random effects {.tabset .tab-pills}

##### By participant

@@

##### By target word

```{r random_effects_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

VarCorr(fit)$target %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = "value") %>% 
	ggplot(aes(term1, term2, fill = value)) +
	geom_tile() +
	coord_fixed() +
	labs(x = "Term 1", y = "Term 2", fill = "Covariance") +
	scale_fill_distiller(palette = "Oranges") +
	theme_bilingual() +
	theme(
		axis.title = element_blank(),
		axis.text.x = element_text(angle = 90)
	)

>>>>

#### Random effects

@@
